---
title: 'Regression: Test Score Evaluation'
author: "Katelyn Patricio"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup}
library(AER)

data("CASchools")

head(CASchools)
```
#### Create variables of average test scores and student to teacher ratio for model creation purposes 
```{r variable creation}
CASchools$avg_test_scores = CASchools$read + CASchools$math / 2
CASchools$ratio = CASchools$students/CASchools$teachers
```

#### Fit a linear regression model to predict test scores based on student to teacher ratio and school funding 
```{r linear model}
m <- lm(CASchools$avg_test_scores ~ CASchools$ratio + CASchools$expenditure)

summary(m)
```

```{r}
m2 <- lm(CASchools$read ~ CASchools$income)

summary(m2)

plot(CASchools$read, CASchools$income)
```

```{r}
# What is the story of this?
m3 <- lm( ~ income + ratio, data = CASchools)

summary(m3)
```


#### Plot individual variables against test scores to visualize relationships
```{r plot average test scores against ratio}
plot(CASchools$avg_test_scores, CASchools$ratio)
```

```{r plot average test scores against expentiture}
plot(CASchools$avg_test_scores, CASchools$expenditure)
```

### Conclusion:
#### Looking at the model, student to teacher ratio has a greater impact on student scores than school funding (expenditure). Each increase in student to teacher ratio decreases test scores by -2.726 points. With a p-value of 0.00347 as well as two stars suggests a significant relationship. On the other hand, each increase in student funding only increases test scores by 0.004 points. Looking at the p-value, it is greater than 0.05 suggesting that this relationship is not meaningful. 
